Closing the gap between statistical and scientific workflows for improved forecasts in ecology

### 2025-03-29 forecastflows.tex
starting wrap-up

>>>>

The misuse of models and misinterpretation of their outcomes (including by the authors) have multiple origins. One cause, almost tautological, is the pressure to publish academic work, which can lower research standards. This challenge extends beyond the scope of this paper, yet we believe that applying an intelligible workflow can promote better research ethics.
This a growing concern, leading to increase in reproducibility and data sharing practices.
However, model development in ecology is still rarely transparent, which limits model understandability and prevents peers from properly identifying potential issues. A significant portion of scientific debate thus becomes lost in methodological considerations rather than advancing our ecological understanding.
